Measuring Software Ticket Quality using Statistical Analysis

### 2017-12-14 proposal/mprop.tex
Complete final draft for the paper

% 1 - 2 pages  structure as work packages (don't bother with a chart).

show how you plan to organize your work, identifying intermediate deliverables and dates.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plainnat}
\bibliography{mprop}
\end{document}

>>>>

The work on the actual project in the second semester will start off 
with deciding and analyzing which repositories to use for ticket data.
We have several popular open source options, such as Apache, Mozilla or
Eclipse, so settling on a couple of options will be the first step in our
research. We believe that this step will be finished \emph{by the end of
January}.

The next step will be to create the scraping, extraction and inspection
tool which will be implemented in either Go or Java. This will be a vital
component of the whole research so we believe that it will be ready to run
\emph{by the end of February}.

Then, concomitantly with the previous work package, we will decide on
what method to use to detect similar tickets. This step will be performed
during the creation of the tool because we can only test efficiency once
we have some tickets to validate our ideas. Thus, the proposed deadline
for this work package is \emph{the end of February} as well.

Following we will run the the tool on the tickets we have collected. This
is expected to be quite trivial once all the other work packages are 
completed as we will simply need to run the application. The expected
deadline is \emph{by 4\textsuperscript{th} of March}.

Then, the actual write-up of the paper will be structured as follows:
  \begin{itemize}
    \item write abstract, introduction, related work - this is expected
      to be completed \emph{by mid March};
    \item write methodology and how we conducted the experiment (collecting
      data, running analysis) - expected to be finished \emph{by the 
      beginning of April};
    \item write results, contributions and conclusion for the paper - 
      we expect to complete it \emph{by 18\textsuperscript{th} of April}.
  \end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plainnat}
\bibliography{mprop}
\end{document}
